### 2021-03-23 ch02_scientific_background/scientific_background.tex
Added details on carbon cycle models to chapter 02

A possible way out is given by numerical climate models, which offer the
possibility to simulate the Earth's climate on a computer. To efficiently
replicate the vastly complex Earth system with finite computational resources,
climate models divide the Earth into a set of \emph{grid cells}. The typical
size of an atmospheric grid cell in a modern-day global climate model is about
$100 \unit{km}$ along the horizontal dimensions (latitude and longitude) and $1
\unit{km}$ along the vertical dimension (pressure level or height). In
addition, the temporal evolution of the Earth system is described using
discrete time steps, which are about $30 \unit{min}$ long in a modern-day
global climate model. For each grid cell and time step, usually a single value
per model variable is given. Examples for such variables provided by a climate
model are the atmospheric prognostic variables velocity (horizontal and
vertical), temperature, specific humidity, pressure and density. These
prognostic variables are related to each other via the \emph{primitive
  equations}, which is a set of partial differential equations that can be
derived from the conservation of momentum, mass, energy and moisture
\autocite{Holton2004}. To progress further in time, these primitive equations
are solved numerically by the dynamical core of the climate models, which
eventually describes the Earth's large-scale atmospheric motion. Similar to
this, many other processes of the Earth system are simulated by the climate
models using other fundamental physical laws and principles. As opposed to
these calculated variables that form the \emph{output} of climate models, the
corresponding \emph{input} is mainly given by the radiative forcing.

@@

Many processes in the Earth system occur at spatial scales much smaller than
the size of a typical grid cell. Illustrative examples for this are clouds,
which are usually much smaller than a $100 \unit{km} \times 100 \unit{km}$ grid
cell, but still play an important role in the overall climate system by
reflecting incoming and outgoing radiation \autocite{Boucher2013}. In order to
approximate these subgrid-scale processes, a concept called
\emph{parameterization} is used. Instead of simulating a process exactly,
parameterizations aim to represent the effect of that process at the grid scale
of the climate model by generating the appropriate forcing terms for the rest
of the system and the rest of the processes \autocite{Gettelman2016}.
Parameterizations are necessary to simulate many processes of the Earth system,
such as surface heat and moisture fluxes, moist convection, turbulent mixing
and radiation \autocite{Holton2004}.

@@

>>>>

A possible way out is given by numerical climate models, which offer the
possibility to simulate the Earth's climate on a computer. To efficiently
replicate the vastly complex Earth system with finite computational resources,
climate models divide the Earth into a set of \emph{grid cells}. The typical
size of an atmospheric grid cell in modern-day global climate models is about
$100 \unit{km}$ along the horizontal dimensions (latitude and longitude) and $1
\unit{km}$ along the vertical dimension (pressure level or height). In
addition, also the temporal evolution of the Earth system is discretized using
time steps that are typically about $30 \unit{min}$ long in modern-day global
climate models. For each grid cell and time step, usually a single value per
model variable is given. Examples for such variables provided by a climate
model are the atmospheric prognostic variables velocity (horizontal and
vertical), temperature, specific humidity, pressure and density. These
prognostic variables are related to each other via the \emph{primitive
  equations}, a set of partial differential equations that can be derived from
the conservation of momentum, mass, energy and moisture \autocite{Holton2004}.
To progress further in time, these primitive equations are solved numerically
by the dynamical core of the climate models, which eventually describes the
Earth's large-scale atmospheric motions. Similar to this, many other processes
of the Earth system are simulated by the climate models using other fundamental
physical laws and principles. As opposed to these calculated variables that
form the output of climate models, the corresponding input is mainly given by
the radiative forcing.

@@

Many processes in the Earth system occur at spatial scales much smaller than
the size of a typical grid cell. Illustrative examples for this are clouds,
which are usually smaller than a $100 \unit{km} \times 100 \unit{km}$ grid
cell, but still play an important role in the overall climate system by
reflecting incoming and outgoing radiation \autocite{Boucher2013}. In order to
reasonably approximate these subgrid-scale processes, a concept called
\emph{parameterization} is used. Instead of simulating a process exactly,
parameterizations aim to represent the effect of that process at the grid scale
of the climate model by generating the appropriate forcing terms for the rest
of the system and the rest of the processes \autocite{Gettelman2016}.
Parameterizations are necessary to simulate many processes of the Earth system,
for example surface heat and moisture fluxes, moist convection, turbulent
mixing and radiation \autocite{Holton2004}.

@@

\subsection{Representation in \aclp{ESM}}
\label{subsec:02:carbon_cycle_representation}

In modern \acp{ESM}, the carbon cycle is usually represented by a land carbon
cycle model and an ocean carbon cycle model that are both coupled to the other
components of the \ac{ESM}. An overarching principle is the conservation of the
total carbon mass in the Earth system \autocite{Gregory2009}, \ie{}
\begin{equation}
  \CE{} = \CA{} + \CL{} + \CO{}.
  \label{eq:02:carbon_balance}
\end{equation}
Here, $\CE{}$ represents the cumulative anthropogenic carbon emissions that are
distributed among the three main carbon reservoirs of the Earth system.
$\CA{}$, $\CL{}$, and $\CO{}$ describe the corresponding changes in these
carbon stores, namely the atmosphere, the terrestrial biosphere (land) and the
ocean, respectively.

Similar to many cloud processes, most carbon cycle--related processes need to
be parameterized in \acp{ESM} since they occur on spatial scales much smaller
than the typical grid cell sizes (see
\cref{subsec:02:numerical_climate_modeling}). For the terrestrial carbon cycle,
the major carbon exchange processes that need to be considered are
photosynthesis, respiration and disturbances, which connect the atmospheric
carbon reservoir and the land carbon reservoir. The latter mainly consists of
the vegetation biomass, litter and soil. The terrestrial carbon exchange
processes are commonly described with \ac{GPP}, \ac{NPP}, \ac{NEP} and
\ac{NBP}, which are all illustrated in \cref{fig:02:carbon_cycle_processes}.
\ac{GPP} describes the total carbon uptake of the vegetation by photosynthesis,
while \ac{NPP} refers to the net carbon gain of the plants after accounting for
autotrophic respiration ($\Ra{}$). \Ac{NEP} additionally considers
heterotrophic respiration ($\Rh{}$) and describes the carbon uptake/release of
the entire ecosystem. Finally, \ac{NBP} describes changes in the long-term
carbon storage of the terrestrial biosphere by including disturbances like
fires \autocite{Ciais2013}.

The different land carbon cycle models integrated into modern \acp{ESM} use a
variety of different parameterizations for the different processes
\autocite{Arora2020}. Examples for the photosynthesis (\ac{GPP}) are given by
\textcite{Farquhar1980} for \ch{C3} plants and \textcite{Collatz1992} for
\ch{C4} plants. The terms \enquote{\ch{C3}} and \enquote{\ch{C4}} refer to the
different metabolic pathways used in the carbon fixation during photosynthesis.
In both cases, the enzyme \ac{RuBisCO} is an important catalyst for the
corresponding chemical reactions. Both parameterizations utilize variables that
are known to affect photosynthesis, such as the availability of light, the
\ac{CO2} concentration, the soil moisture and the temperature.

### 2021-03-23 ch06_paper_gpp/paper_gpp.tex
Added details on carbon cycle models to chapter 02

\subsection{Constraining the \texorpdfstring{\acs{CO2}}{CO2} Fertilization
  Effect (Step 1)}
\label{subsec:06:step_1}

@@

In contrast to \textcite{Wenzel2016}, instead of idealized simulations we apply
the presented emergent constraint on the emission-driven \acs{RCP}8.5
simulation \autocite{Riahi2011} and examine whether it still holds for this
simulation where forcings other than \ac{CO2} also change. Moreover, we
consider the global mean \ac{GPP} change instead of the \ac{GPP} change in the
northern extratropics as in \textcite{Wenzel2016}. Due to the strong annual
mixing of \ac{CO2} in the atmosphere, the change in the \ac{CO2} seasonal cycle
amplitude at \ac{KUM} is representative for the whole globe. Thus, we apply
this emergent constraint to the global mean \ac{GPP} change. However, we note
that this approach might introduce errors since the \ac{CO2} fertilization
effect could be different for tropical and extratropical ecosystems due to
nutrient limitations and the temperature dependence of Rubisco kinetics
\autocite{CraftsBrandner2000} in the tropics. Nevertheless, we argue that we
can use the constraint if the emergent relationship still holds within our
considered framework (the \acs{RCP}8.5 scenario simulated by the \acs{CMIP}5
models).

>>>>

\subsection{Constraining the \texorpdfstring{\acs{CO2}}{\ch{CO2}} Fertilization
  Effect (Step 1)}
\label{subsec:06:step_1}

@@

In contrast to \textcite{Wenzel2016}, instead of idealized simulations we apply
the presented emergent constraint on the emission-driven \acs{RCP}8.5
simulation \autocite{Riahi2011} and examine whether it still holds for this
simulation where forcings other than \ac{CO2} also change. Moreover, we
consider the global mean \ac{GPP} change instead of the \ac{GPP} change in the
northern extratropics as in \textcite{Wenzel2016}. Due to the strong annual
mixing of \ac{CO2} in the atmosphere, the change in the \ac{CO2} seasonal cycle
amplitude at \ac{KUM} is representative for the whole globe. Thus, we apply
this emergent constraint to the global mean \ac{GPP} change. However, we note
that this approach might introduce errors since the \ac{CO2} fertilization
effect could be different for tropical and extratropical ecosystems due to
nutrient limitations and the temperature dependence of \ac{RuBisCO} kinetics
\autocite{CraftsBrandner2000} in the tropics. Nevertheless, we argue that we
can use the constraint if the emergent relationship still holds within our
considered framework (the \acs{RCP}8.5 scenario simulated by the \acs{CMIP}5
models).
